Updates on the Exoplanet Orbit Database

### 2014-01-24 draft/ms.tex
Conflict test: modify MASS description.

MASS: Previously, we only reported the minimum mass (MSINI) of the planets. We now report mass of the planet in the unit of Jupiter mass. If a planet is discovered by transit, the planet mass is given by the literature. However, if a planet is detected by radial velocity method, the minimum mass is given in which case we calculate the mass by dividing the minimum mass by the orbit inclination. MASS is set to MSINI if the orbital inclination is not given and the MASSREF is set to ``Set to MSINI; I unknown''

MASS: we use mass-radius relation to get mass. =>stellar mass?

>>>>

MASS: Previously, we only reported the minimum mass (MSINI) of the
planets. We now report mass of the planet in the unit of Jupiter
mass. If a planet is discovered by transit, the planet mass is given
by the literature. However, if a planet is detected by radial velocity
method, the minimum mass is given in which case we calculate the mass
by dividing the minimum mass by the orbit inclination. MASS is set to
MSINI if the orbital inclination is not given and the MASSREF is set
to ``Set to MSINI; I unknown''.

MASS: For KOIs without MSINI measured, Exoplanet Archive reports MASS
based on converting radius into mass.
